A Tutorial on Tailored Simulation-Based Power Analysis for Experimental Designs with Generalized Linear Mixed Models

### 2024-03-27 docs/manuscript.Rmd
add susannes paragraph on the iterative exchange with domain experts

@@

```{r margdist1, fig.cap="(ref:margdist1-caption)"}
library(tidyverse)
library(ggdist)
dat <- simulate(n_subjects = 2000, n_items = 2000, sd_u0s = 0.5, sd_u0i = 0.5)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

>>>>

##### PRACTICE

All parameter values in our present case study have been determined from results from related prior work and repeated discussions with our affiliated domain experts in Radiology to validate our assumptions.
Initially, we reviewed the literature to establish a reasonable baseline performance rate for examining head CT scans for ICH. Existing studies indicate that radiologists typically demonstrate high accuracies, often exceeding or hovering around 90%, while interns have been shown to perform below 80%, and medical students fall even shorter.
For simplicity, we assumed plausible probability values of .90 for experts and .70 for non-experts, respectively.
Our experts confirmed that these values are realistic baselines for reviewing diverse head CT images without AI assistance. Subsequently, we consulted several published papers investigating the effect of correct and incorrect advice on decision-making performance in other settings.
From their findings, we inferred that both experts and non-experts would benefit from correct and suffer losses from incorrect advice.
However, the magnitude of these effects would be substantially greater for non-experts, given their demonstrated reliance on advice compared to experts.
We further validated the plausibility of our estimated gains and losses with the collaborating radiologists.
For our simulation, we used the probabilities of average participants to solve an average case, as shown in Table 1.

@@

```{r margdist1, fig.cap="(ref:margdist1-caption)"}
library(tidyverse)
library(ggdist)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0s = 0.5, sd_u0i = 0.5)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
library(tidyverse)
library(ggdist)
dat <- simulate(n_subjects = 3000, n_items = 3000, sd_u0s = 0.5, sd_u0i = 0.5)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>%
  group_by(condition) %>%
  summarize(freq_y_1 = sum(y_bin) / n())
```
